### 2014-03-09 src/intro.Rnw
update

% 1. Describe the problem
% 2. State your contributions
Mutation analysis is a method of evaluation of quality of test-suites. It involves generation
of  mutants by making syntactic changes to the program. First (higher) order mutants
have one (more) syntactic distance to the origianl program.
Mutants are used to evaluate the effectiveness of test-suites 
~\cite{lipton1971fault, ammann2008introduction}.
Studies like ~\cite{andrews2005mutation} have shown that mutation score 
are predictors of the real fault detection of a test suits.

A major impediment to wider adoption of mutation analysis is its high computational cost.
Set of first oder mutants of a moderate size program can be very large, 
which renders mutation analysis of a test-suite against all the first
order mutants prohibitively time-consuming.

@@

Selective mutation strategies attempt to select a representative subset of operators based 
on heuristics and statistical analysis. They suggest applying these subsets instead of the 
applying the whole gamut of mutation operators~\cite{offutt1993anexperimental,untch2009onreduced}.

Sampling strategies seek to randomly select smaller representative mutants.
This was investigated first by Acreed~\cite{acree1980mutation} and Budd~\cite{budd1980mutation},
who proposed using only $x$\% of the mutants produced. The studies by Wong and
Mathur, found that random sampling with ratio as low as 10\% could provide
accurate results~\cite{jia2011analysis}.

@@

While all these areas of research has been relatively successful in reducing the number of mutants
produced, there has been comparitively few studies that compares the approaches taken. The studies
that has been attempted so far, has been limited by the comparitively small number of sampled projects.

\noindent\textbf{Contribution.} Contributions of this paper are he following.
\begin{itemize}
\item It compares a large number of various mutation sampling and selection strategies (Section~\ref{sec:analysis}).
\item It seek sto improve the statistical confidence in our results by utilizing a much larger sample of projects
      (188 projects) from the open source repository at Github~\cite{github}, using both original and automatically
      generated test-suites using Randoop~\cite{randoop} (Section~\ref{sec:methodology}). 
\item It analyses the results and suggest strategies (Section~\ref{sec:results}).
\end{itemize}

@@

% \begin{comment}
%   These approach relies on the fact that some of the mutagens generate a large number of variants, and hence produce highly redundant test cases. Previous research suggested that elimination of mutagens with high fertility results in the reduction of total number of mutations produced, and hence reduces the computational requirements.
%
%   % TODO check the survey again on selective mutation.
%
%   It was recently questioned whether this approach indeed resulted in a tangible improvement over random selection of mutants\cite{zhang2010operator}, which did not find operator based selection to be better than random selection.
%
%
%   Another research, initially by Unch\cite{untch2009onreduced} and recently by Deng et al.\cite{deng2013empirical} suggests using software deletion operator since it produces the least number of mutants (smallest neighborhood). The researchers were able to obtain a close approximation of original mutant score with significant savings with this approach.
%
%   However, our previous research suggests that mutation coverage is closely predicted by statement coverage, this suggests that any criteria that forces accounting of the impact of each statement should provide a close approximation to the full mutation score. Hence, our research suggests that SDL works because it forces accounting of each line, and a random sampling criteria that provides the same criteria should result in similar results.
%
%   In our analysis, we find that a random sampling approach that randomly chose a single mutant per line was found to have a better correlation with the full mutation score than that obtained by SDL. Further it was also found that the mutation score produced by random sampling was closer to the full mutation score than that produced by SDL.
%
% Order of most fertile operators for N-selective operator selection.
% NON_VOID_METHOD_CALLS
% NEGATE_CONDITIONALS
% REMOVE_CONDITIONALS
% DELETE_CONDITIONALS
% RETURN_VALS
% INLINE_CONSTS
% CONSTRUCTOR_CALLS
% EXPERIMENTAL_MEMBER_VARIABLE
% VOID_METHOD_CALLS
% MATH
% CONDITIONALS_BOUNDARY
% INCREMENTS
% REMOVE_INCREMENTS
% RMSWITCH
% EXPERIMENTAL_SWITCH
% INVERT_NEGS
%
% \end{comment}
%
%
% NON_VOID_METHOD_CALLS VOID_METHOD_CALLS CONSTRUCTOR_CALLS
% NEGATE_CONDITIONALS REMOVE_CONDITIONALS DELETE_CONDITIONALS CONDITIONALS_BOUNDARY
% RETURN_VALS INLINE_CONSTS EXPERIMENTAL_MEMBER_VARIABLE
% MATH INCREMENTS REMOVE_INCREMENTS INVERT_NEGS
% RMSWITCH EXPERIMENTAL_SWITCH

>>>>

% 1. Describe the problem
% 2. State your contributions
Mutation analysis is a method of evaluation of quality of test-suites. It involves producing
a family of mutants with simple differences from the original program, and evaluating the
effectiveness of test-suites against the these mutants~\cite{lipton1971fault, ammann2008introduction}.
Previous research~\cite{andrews2005mutation} suggests that mutations thus introduced behave
in a fashion similar to the real-faults with respect to the difficulty of detection.

One of the impediments to wider adoption of mutation analysis is its high computational cost.
The set of simple mutants of a moderate sized program can be very large, and renders
mutation analysis prohibitively time-consuming.

@@

Selective mutation strategies attempt to select a representative subset of operators based
on heuristics and statistical analysis, and applying this subset of operators to generate mutants
instead of applying the whole gamut of mutation operators~\cite{offutt1993anexperimental,untch2009onreduced}.

Sampling strategies seek to randomly select smaller representative mutants.
This was investigated first by Acree~\cite{acree1980mutation} and Budd~\cite{budd1980mutation},
who proposed using only $x$\% of the mutants produced. The studies by Wong and
Mathur found that random sampling with ratio as low as 10\% could provide
accurate results~\cite{jia2011analysis}.

@@

A few recent works~\cite{zhang2010icse,zhang2013ase} have investigated the relative merits of
random sampling strategies and operator selection. It was found that while random sampling can
generally perform equal to or better than operator selection, a strategy that combined random
sampling with program elements paid superior dividends.

However, as pointed out by Zhang et al.~\cite{zhang2013ase}, the field has a serious lacuna in
large scale research, both in the size of the programs studied, and in the number and diversity
of programs, which reduces our confidence in the espoused results. This is true both for
selective mutation, sampling strategies, and also for comparatively newer studies that attempt
to join them together.  This is particularly worrisome if mutation analysis is to gain wider
acceptance among testing professionals. Further quite a few of the influential studies has been
conducted on older programming languages such as Fortran with operators specific to it, which
may not carry over to the newer and popular languages such as Java. Finally, with the modern
research into the ``do-smarter'' approach which allows byte code based mutation -- thus eliminating
the compilation step -- operators based on source code modification is no longer be applicable, and
their equivalents in the bytecode needs to be found and compared with other approaches. A detailed
discussion of these issues can be found in Section~\ref{sec:relatedwork}.

% RAHUL>AMIN: I find the non-bulleted contributions better flowing as I can work the references
% to other sections into it. Let me know if you have a better idea (As it stands neither my
% previous wording, nor your bulleted list reads good)
We have attempted to rectify this situation with a large scale study of industrial programs.
As detailed in Section~\ref{sec:methodology}, we sample 188 real world Java programs from Github, with
size ranging from 50loc to 100kloc, which makes our inferences relatively strong, and widely applicable.
We provide the results from running both original human generated test-suites, and also programmatically
generated test-suites, increasing the applicability of our findings to both researchers who seek to
compare test-suites quickly, and to industrial software testers who might be looking for a way to reduce
the time of their build cycle when using mutation coverage. The Section~\ref{sec:methodology} discusses
the sampling strategies attempted, and the operator selection strategies in detail, and the results of
our experiment are given in Section~\ref{sec:results}, followed by detailed discussion of what it implies
in section ~\ref{sec:discussion}. The research concludes in Section~\ref{sec:conclusion}.

Our specific contributions in this paper are listed as follows:

\begin{itemize}
\item Our study is the largest so far in terms of both the size of programs involved, and the number of
  programs analyzed for ``do-fewer'' strategies, which makes our inferences stronger and widely applicable.
\item We compare a large number of ``do-fewer'' strategies, especially with respect to their predictive
  power over the final mutation score.
\item Our sampling strategies include some that were suggested by other researchers, and also a few novel
  strategies that has not been published elsewhere.
\item Our recommendations are valid for both testing researchers who might be comparing programmatically
  generated test-suites, and software testing professionals working on real test-suites.
\end{itemize}
%We make the following contributions:
%\begin{itemize}
%\item We compare a large number of mutation sampling and selection strategies (Section~\ref{sec:analysis}).
%\item It seek sto improve the statistical confidence in our results by utilizing a much larger sample of projects
%      (188 projects) from the open source repository at Github~\cite{github}, using both original and automatically
%      generated test-suites using Randoop~\cite{randoop} (Section~\ref{sec:methodology}). 
%\item It analyses the results and suggest strategies (Section~\ref{sec:results}).
%\end{itemize}

@@

% \begin{comment}
% Order of most fertile operators for N-selective operator selection.
% NON_VOID_METHOD_CALLS
% NEGATE_CONDITIONALS
% REMOVE_CONDITIONALS
% DELETE_CONDITIONALS
% RETURN_VALS
% INLINE_CONSTS
% CONSTRUCTOR_CALLS
% EXPERIMENTAL_MEMBER_VARIABLE
% VOID_METHOD_CALLS
% MATH
% CONDITIONALS_BOUNDARY
% INCREMENTS
% REMOVE_INCREMENTS
% RMSWITCH
% EXPERIMENTAL_SWITCH
% INVERT_NEGS
%
% \end{comment}
%
% NON_VOID_METHOD_CALLS VOID_METHOD_CALLS CONSTRUCTOR_CALLS
% NEGATE_CONDITIONALS REMOVE_CONDITIONALS DELETE_CONDITIONALS CONDITIONALS_BOUNDARY
% RETURN_VALS INLINE_CONSTS EXPERIMENTAL_MEMBER_VARIABLE
% MATH INCREMENTS REMOVE_INCREMENTS INVERT_NEGS
% RMSWITCH EXPERIMENTAL_SWITCH

### 2014-03-09 src/paper.Rnw
update

\begin{comment}
<<setup, include=FALSE, cache=FALSE, message=FALSE, echo=FALSE>>=
clean <- function(x)sub('CONSTRUCTOR','CONSTR',sub('RETURN','R',sub('INCREMENTS','INC',sub('VOID','V',sub('CONDITIONAL','COND',sub('NON','N',sub('VARIABLE','VAR',sub('MEMBER','MEM',sub('DELETE_','D_',sub('REMOVE_','R_',sub('NEGATE_','N_',sub('_CALLS','',sub('EXPERIMENTAL_','E_',x)))))))))))))
#options(warn=-1)
options(digits=3)
opts_chunk$set(fig.path='figure/twocolumn-', fig.align='center', fig.show='hold', echo=FALSE)
render_listings()
logit<-function(x) log(x/(1-x))
require(reshape2)
require(xtable)
require(ggplot2)
require(Mutsel)
@
<<chunk-hook, echo=2>>=
<<setup>>
v=data(package='Mutsel')
data(list = v$results[,3])
original.stats.df <- stats.df # save it
o.f <- function(x) subset(x, kind == 'original')
r.f <- function(x) subset(x, kind == 'randoop')
o.stats.df <- o.f(stats.df)
r.stats.df <- r.f(stats.df)
@
\end{comment}
% 10 pages for the main text + 1 for references.
<<intro, child='intro.Rnw'>>=
@
<<related, child='related.Rnw'>>=
@
<<methodology, child='methodology.Rnw'>>=
@
<<analysis, child='analysis.Rnw'>>=
@
<<results, child='results.Rnw'>>=
@
<<results, child='conclusion.Rnw'>>=
@

>>>>

\begin{comment}
<<setup, include=FALSE, cache=FALSE, message=FALSE, echo=FALSE>>=
clean <- function(x)sub('CONSTRUCTOR','CONSTR',sub('RETURN','R',sub('INCREMENTS','INC',sub('VOID','V',sub('CONDITIONAL','COND',sub('NON','N',sub('VARIABLE','VAR',sub('MEMBER','MEM',sub('DELETE_','D_',sub('REMOVE_','R_',sub('NEGATE_','N_',sub('_CALLS','',sub('EXPERIMENTAL_','E_',x)))))))))))))
#options(warn=-1)
options(digits=3)
opts_chunk$set(fig.path='figure/twocolumn-', fig.align='center', fig.show='hold', echo=FALSE)
render_listings()
logit<-function(x) log(x/(1-x))
require(reshape2)
require(xtable)
require(ggplot2)
require(Mutsel)
@
<<chunk-hook, echo=2>>=
<<setup>>
v=data(package='Mutsel')
data(list = v$results[,3])
original.stats.df <- stats.df # save it
o.f <- function(x) subset(x, kind == 'original')
r.f <- function(x) subset(x, kind == 'randoop')
o.stats.df <- o.f(stats.df)
r.stats.df <- r.f(stats.df)
@
\end{comment}
% 10 pages for the main text + 1 for references.
<<intro, child='intro.Rnw'>>=
@
<<related, child='related.Rnw'>>=
@
<<methodology, child='methodology.Rnw'>>=
@
<<analysis, child='analysis.Rnw'>>=
@
<<results, child='results.Rnw'>>=
@
<<results, child='discussion.Rnw'>>=
@
<<conclusion, child='conclusion.Rnw'>>=
@
